%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Eric}{Hayden Campbell}{ \urlstyle{same}\url{https://ericthewry.github.io} \\
\href{mailto:ehc86@cornell.edu}{ehc86@cornell.edu} | 909.343.9392
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 


\subsection{Cornell University}

\descript{Ph.D. in Computer Science}

  
    \location{Expected May 2022 | Ithaca, NY}
    \descript{M.Sc. in Computer Science}
    \location{Expected May 2019 | Ithaca, NY}
  

  Conc. in Programming Languages
  \sectionsep

\subsection{Pomona College}

\descript{B.A. in Computer Science}

  
    \descript{B.A. in Mathematics}
    \location{Graduated May 2017 | Claremont, CA}
  

  Conc. in Programming Languages
  \sectionsep

\subsection{International School}

\subsection{of Amsterdam}

\descript{International Baccalaureate}

  \location{Graduated May 2013 | Amsterdam, The Netherlands}

  Conc. in Mathematics
  \sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ericthewry}{\custombold{ericthewry}} \\
LinkedIn://  \href{https://www.linkedin.com/in/eric-campbell-ba339490/}{\custombold{ericcampbell}} \\
StackOverflow:// \href{https://stackoverflow.com/users/8202530/ericthewry}{\custombold{ericthewry}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Kleene Algebra \textbullet{}
Category Theory \textbullet{}
Advanced Programming Languages \textbullet{}
Network Programming Languages \textbullet{}
Advanced Systems
\sectionsep

\subsection{Undergraduate}
Software Foundations (Coq) \textbullet{}
Programming Languages \textbullet{}
Senior Seminar (Security, Programmig Languages, \& Ethics) \textbullet{}
Computability \& Logic %% \\
%% Computational Statistics \\     
%% Number Theory \& Cryptography
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
OCaml \textbullet SMTLIB \textbullet Haskell \textbullet{} Coq \textbullet{} Java \textbullet{} Python \textbullet{} Ruby on Rails \textbullet{} \LaTeX \\ 
\location{Over 1000 lines:}
R \textbullet{} SQL \textbullet{} Java \textbullet{} bash \\
\sectionsep

% \subsection{Foreign Language}
% Professional French \textbullet{} Survival Dutch
% \sectionsep

%% \subsection{Other}
%% Guitar \textbullet{} Voice \textbullet{} Espresso \\
%% Ballroom Dance \textbullet{} Linguistics


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Industry Experience}

\runsubsection{Fujitsu Laboratories of America}
\descript{| Research Intern}
\location{May 2018 - Aug 2018 | Sunnyvale, CA}
\vspace{\topsep}
\begin{tightemize}
\item Developed time-based procedure for detecting anomalies in networks.
\item Analyzed synthetic topologies running GoBGP configurations.
\item Detected a bug in GoBGP
\end{tightemize}
 \sectionsep
\runsubsection{Originate}
\descript{| Software Engineering Intern }
\location{May 2015 – Aug 2015 | San Francisco, CA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
  \item Developed Massive multi-user Ruby on Rails \& Coffeescript applications.
  \item Won Nation-wide intern hackathon.
\end{tightemize}
\sectionsep

% \runsubsection{Gladly,Inc}
% \descript{| Software Engineering Intern }
% \location{May 2014 – Aug 2014 | Palo Alto, CA}
% \begin{tightemize}
% \item Improved user downloads by 40\% by redesinging the website
%   front-end.
% \item Developed front-end widgets for the browser extension.\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Selected Publications}


\runsubsection{P4Cub: A Little Language for Big Routers}
\descript{Rudy Peterson, <b>Eric Hayden Campbell</b>, John Chen, Natalie Isak, Calvin Shyu, Ryan Doenges, Parisa Ataei, and Nate Foster}


\location{CPP|Jan 2023}


P4Cub is a new intermediate representation (IR) for the P4 programming language that is designed to facilitate the development of certified tools.
\sectionsep



\runsubsection{Kleene Algebra Modulo Theories}
\descript{Michael Greenberg, Ryan Beckett, and <b>Eric Hayden Campbell</b>}


\location{PLDI|June 2022}


Generate Soundness proofs, Completeness proofs, and Decision procedures for KAs plus a Sound, Complete and Decidable, client theory.
\sectionsep



\runsubsection{Dependently-Typed Data Plane Programming}
\descript{Matthias Eichholz, <b>Eric Hayden Campbell</b>, Matthias Krebs, Nate Foster,  Mira Mezini}


\location{POPL|January 2022}


Develop a dependent refinement type system for P4 with a liquid-style Z3 backend to prohibit undefined behavior
\sectionsep



\runsubsection{Avenir: Managing Data Plane Heterogeneity via Control Plane Synthesis}
\descript{<b>Eric Hayden Campbell</b>, William T. Hallahan, Priya Srikumar, Carmelo Cascone, Jed Liu, Vignesh Ramamurthy, Hossein Hojjat, Ruzica Piskac, Robert Soulé, J. Nathan Foster}


\location{NSDI|April 2021}


Employ program synthesis to translate abstract switch operations into target switch operations
\sectionsep



\runsubsection{Epistemic Semantics in Guarded String Models}
\descript{<b>Eric Hayden Campbell</b>, Mats Rooth}


\location{SCiL|February 2021}


Extend Kleene Algebra with Tests to model epistemic semantics of modal verbs in natural English
\sectionsep



\runsubsection{How to Avoid Making a Billion-Dollar Mistake: Type-Safe Data Plane Programming with SafeP4}
\descript{Matthias Eichholz, <b>Eric Hayden Campbell</b>, Nate Foster, Guido Salvaneschi, Mira Mezini}


\location{ECOOP|July 2019}


Develop a Type System for P4 that prohibits references to invalid headers. Surveys open source programs to identify real-world bugs that our type system prevents
\sectionsep



\runsubsection{Injecting Finiteness to Prove Completeness for Finite Linear Temporal Logic}
\descript{<b>Eric Hayden Campbell</b>, Michael Greenberg}


\location{arXiv:2107.06045}


Proved Soundness, Completeness and Decidability for Finite-Trace Linear Temporal Logic. Developed a decision procedure for the logic. Proved the axiomatization equivalent to the temporal axioms in Temporal NetKAT, making a completeness proof possible for TNK.
\sectionsep



\runsubsection{Infiniteness and Linear Temporal Logic}
\descript{<b>Eric Hayden Campbell</b>, advised by Michael Greenberg}


\location{Pomona College|May 2017}


Proved Soundness, Completeness and Decidability for Finite-Trace Linear Temporal Logic. Developed a decision procedure for the logic. Proved the axiomatization equivalent to the temporal axioms in Temporal NetKAT, making a completeness proof possible for TNK.
\sectionsep



\runsubsection{Constructing Integer Matrices with Integer Eigenvalues}
\descript{Christopher Towse and <b>Eric Hayden Campbell</b>}


\location{The Mathematical Scientist, UK|June 2016}


Developed a construction algorithm for Integer Matrices with Integer Eigenvalues (IMIEs). Created a web app to create an IMIE from an arbitrary input matrix.
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Projects}

% \runsubsection{Databases @ Pomona College}
% \descript{| Research Assistant}
% \location{Jan 2016 – Aug 2016| Claremont, CA}
% Worked with \textbf{\href{http://www.cs.pomona.edu/~mwu/files/bio.htm}{Professor Melanie Wu}} on the development of \textbf{QuickTSI}, a fast query system for finding (partial) subgraph isomorphisms on temporal graphs.
% \sectionsep

%% \runsubsection{\href{http://mathswipe.com}{MathSwipe}}
%% \descript{| Technical Lead}
%% \location{Led a distributed team to build CoffeeScript puzzle game. Chose technologies, delegated tasks, and contributed majority of code.}
%% \sectionsep

%% \runsubsection{RoomDraw}
%% \descript{| Technical Lead}
%% \location{Ruby on Rails \& PostgreSQL application to automate the Pomona College room-draw process. Algorithmically assigns rooms based on preferences.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Teaching
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Teaching} 

\begin{tabular}{llll}
  
    Spring 2018 & TA & OOP and Data Structures & Cornell University \\
  
    Fall 2017 & TA & OOP and Data Structures & Cornell University \\
  
    Spring 2017 & TA & Database Systems & Pomona College \\
  
    Fall 2016 & TA & Programming Languages & Pomona College \\
  
    Spring 2016 & Head TA & Intro to CS & Pomona College \\
  
    Fall 2015 & TA & Intro to CS & Pomona College \\
  
\end{tabular}


\sectionsep

\end{minipage} 
\end{document}

