%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Eric}{Campbell}{ \urlstyle{same}\url{https://ericthewry.github.io} \\
\href{mailto:ehc86@cornell.edu}{ehc86@cornell.edu} | 909.343.9392
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Cornell University}
\descript{PhD in Computer Science}
\location{Expected May 2022 | Ithaca, NY}
Conc. in Programming Languages \\
Department of Computer Science
\sectionsep

\subsection{Pomona College}
\descript{BS in Computer Science, BS in Mathematics}
\location{Grad. May 2017 | Claremont, CA}
Conc. in Programming Languages \\
Department of Computer Science \\
\sectionsep

\subsection{International School}
\subsection{of Amsterdam}
\location{Grad. May 2013 | Amsterdam, The Netherlands}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ericthewry}{\custombold{ericthewry}} \\
LinkedIn://  \href{https://www.linkedin.com/in/eric-campbell-ba339490/}{\custombold{ericcampbell}} \\
StackOverflow:// \href{https://stackoverflow.com/users/8202530/ericthewry}{\custombold{ericthewry}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
%% \subsection{Graduate}
%% Advanced Machine Learning \\
%% Open Source Software Engineering \\
%% Advanced Interactive Graphics \\
%% Compilers + Practicum \\
%% Cloud Computing \\
%% \sectionsep

\subsection{Undergraduate}
Software Foundations (Coq) \\
Programming Languages \\
Senior Seminar (Security, Programming Languages, \& Ethics) \\
Computability \& Logic \\
Computational Statistics \\
Number Theory \& Cryptography
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Haskell \textbullet{} Coq \textbullet{} Java-/CoffeeScript   \\
Python \textbullet{} Ruby on Rails \textbullet{} \LaTeX \textbullet{} bash \\ 
\location{Over 1000 lines:}
OCaml \textbullet{} R \textbullet{} MySQL \textbullet{} C++ \textbullet{} Java \\
\location{Familiar:}
Elm \textbullet{} C  \textbullet{} HTML/CSS  \textbullet{} iOS
\sectionsep

\subsection{Foreign Language}
Professional French \textbullet{} Survival Dutch
\sectionsep

\subsection{Other}
Guitar \textbullet{} Voice \textbullet{} Espresso \\
Ballroom Dance \textbullet{} Linguistics


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Industry Experience}

\runsubsection{Originate}
\descript{| Software Engineering Intern }
\location{May 2015 – Aug 2015 | San Francisco, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
  \item Developed Massive multi-user Ruby on Rails \& Coffeescript applications.
  \item Won Nation-wide intern hackathon.
\end{tightemize}
\sectionsep

\runsubsection{Gladly,Inc}
\descript{| Software Engineering Intern }
\location{May 2014 – Aug 2014 | Palo Alto, CA}
\begin{tightemize}
\item Worked on the Tab for a Cause team in JQuery and Python to redesign the front-end implementation of the website.
\item Improved new-user downloads by 30\%.
\item Developed front-end widgets for the browser extension.\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Programming Languages @ Pomona College}
\descript{| Research Assistant}
\location{August 2016 – Present | Claremont, CA}
Worked with \textbf{\href{http://www.cs.pomona.edu/~michael/}{Professor Michael Greenberg}} to prove Soundness and Completeness for Finite-Trace Linear Temporal Logic (LTL$_f$). Developed a decision procedure for the logic. Proved the axiomatization equivalent to the temporal axioms in Temporal Net\textsc{kat} (TNK), resulting in a completeness proof for TNK. Resulted in my \href{https://ericthewry.github.io/pdfs/thesis.pdf}{\custombold{thesis}}, a submission to POPL 2018, and a submission to FoSSaCS 2018.
\sectionsep

\runsubsection{Databases @ Pomona College}
\descript{| Research Assistant}
\location{Jan 2016 – Aug 2016| Claremont, CA}
Worked with \textbf{\href{http://www.cs.pomona.edu/~mwu/files/bio.htm}{Professor Melanie Wu}} on the development of \textbf{QuickTSI}, an fast algorithm for finding (partial) subgraph isomorphisms on temporal graphs (graphs with time-varying edges). Built an in-memory database prototype implementing this algorithm.
\sectionsep

\runsubsection{Number Theory @ Scripps College}
\descript{| Research Assistant}
\location{December 2015 - July 2017 | Claremont, CA}
Worked with \textbf{\href{http://www.scrippscollege.edu/academics/faculty/profile/christopher-towse}{Professor Christopher Towse}} to develop a construction algorithm for Integer Matrices with Integer Eigenvalues (IMIEs). Created \href{http://ericthewry.github.io/integer_matrices}{a web app} to create an IMIE from an arbitrary input matrix. Results published in The Mathematical Scientist.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Independent Projects}
\runsubsection{\href{http://mathswipe.com}{MathSwipe}}
\descript{| Technical Lead}
\location{Manage a distributed team to build CoffeeScript puzzle game. The game randomly generates boards with arithmetic problems to solve by swiping. Developed an algorithm to ensure that every random board has a solution.}
\sectionsep

\runsubsection{RoomDraw}
\descript{| Technical Lead}
\location{Ruby on Rails \& PostgreSQL application to automate the Pomona College room-draw process. Algorithmically assigns rooms based on preferences.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Teaching
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Teaching} 

\begin{tabular}{llll}
  Spring 2017 & TA      & Database Systems & Pomona College \\
  Fall   2016 & TA      & Programming Languages & Pomona College \\
  Spring 2016 & Head TA & Intro to CS & Pomona College \\
  Fall   2015 &  TA     & Intro to CS & Pomona College
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}
